\MakeUppercase{The Structure of $k$-Planar Graphs}

### 2019-07-09 k-planar.tex
Fixed serious typo ---- in Theorem 2

\begin{thm}
\label{kPlanarBasic}
Every $k$-planar graph is a subgraph of $H\boxtimes P$, for some graph $H$ of treewidth $(18k^3+30k)\binom{k+4}{3}-1$ and for some path $P$. 
\end{thm}

>>>>

\begin{thm}
\label{kPlanarBasic}
Every $k$-planar graph is a subgraph of $H\boxtimes P$, for some graph $H$ of treewidth $(18k^2+30k)\binom{k+4}{3}-1$ and for some path $P$. 
\end{thm}
